---
title: "Advanced ggplot2 homework"
output: html_notebook
---

```{r}
library(tidyverse)

```


```{r}
library(CodeClanData)
```

```{r}
revenue <- qb_revenue_breakdown
monthly_sales <- qb_monthly_sales
competitors <- qb_competitors
device_data <- qb_device_data

```




```{r}
col_scheme <- c("#E89FE9", "#50434F", "#B6A7B5", "#F9A472", "#BD7040")

```

## Question 1. Take the data in the dataset qb_revenue_breakdown and make a stacked bar chart showing the sources of revenue across the two years in the dataset.

```{r}
ggplot(revenue) +
  geom_bar(position="stack", aes(x= Product, fill=Year)) +
  ggtitle("Sources of Revenue From 2018 to 2019")

```


## Question 2. Make a line chart showing monthly sales of the “flagship product” - the ‘KwikBit Unit 1’ - over the last year. This data is inside qb_monthly_sales, but you will need to use filter() or subset() (base R).

```{r}
monthly_sales_2 <- monthly_sales %>%
  filter(Cashflow == "Kwikbit Unit 1 Sales")

ggplot(monthly_sales_2) +
  geom_line(aes(x=Date, y=Amount)) +
  ggtitle("Monthly Sales of KwikBit Unit 1 From 2018 to 2019")

```

## Question 3. Make a line chart showing monthly revenue and costs over the last year. This data is also in qb_monthly_sales.

```{r}
sales_revenue_costs <- monthly_sales %>%
  filter(Cashflow != "Kwikbit Unit 1 Sales")

ggplot(sales_revenue_costs) +
  geom_line(aes(x=Date, y=Amount)) +
  ggtitle("Monthly Revenue and Costs From 2018 to 2019")

```


## Question 4. Show annual sales of personal fitness trackers over the last 5 years broken down by company as a ribbon plot (use geom_area). This data is in qb_competitors.

```{r}
ggplot(competitors) +
  geom_area(aes(x=Year, y=Revenue, fill=Company)) +
  ggtitle("Competitors Annual Sales of Personal Fitness Trackers Over Last 5 Years")
```


## Question 5. Now show the sales from the four competitors as a line graph. Include an extra layer that shows the data points used to make the lines.

```{r}
ggplot(competitors) +
  geom_line(aes(x=Year, y=Revenue, fill=Company)) +
   geom_point(aes(x = Year, y = Revenue)) +
  xlab("Year") +
  ylab("Revenue") +
  ggtitle("Competitors Annual Sales of Personal Fitness Trackers Over Last 5 Years")


```


## Question 6.Now the company wants to compare the number of steps that their device counts vs. their competitors. Make a line graph of the number of steps throughout time, and use faceting to compare between companies and people. The data for this is in qb_device_data.

```{r}
device_data_2 <- device_data %>%
  mutate(time_hours = hours + mins/60)

```


```{r}
ggplot(device_data_2) +
  geom_line(aes(x=time_hours, y=counts)) +
  xlab("Time in hours") +
  ylab("Steps") +
  ggtitle("Number of Steps Counted for quikbit1 vs. Competitors") +
  facet_wrap(device ~ id)

```


