---
title: "Introduction to ggplot2 homework"
output: html_notebook
---

## Question 1. Load in the libraries you need, and look at the backpack data. Take note of variable names and dimensions.

```{r}
library(tidyverse)
library(CodeClanData)
```

```{r}
backpack_data <- backpack
head(backpack_data)
```


## Question 2.What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution.

```{r}
ggplot(backpack_data) +
  aes(x = backpack_weight) +
  geom_histogram() +
  xlab("Backpack Weight in Kg") +
  ylab("Number of students") +
  ggtitle("Distribution of backpack weights amongst students")
  theme_minimal()
```

The majority of students have backpacks weighing between 4kg and 21kg.  The highest backpack weight is 35kg and the lowest is 2kg. 


## Question 3.Are there differences in backpack weight between sex?

```{r}
ggplot(backpack_data) +
  aes(x=sex, y=backpack_weight) +
  geom_line() +
  geom_point()+
  ggtitle("Backpack weights for males and females")+
  ylab("Backpack weight in Kg")

```
The majority of males and females have backpack weights of between 2 and 25kg.  There is one male who has a heavier backpack weight of 35kg.  Generally males and females have similar backpack weights as backpack weight is probably influenced by which items are necessary for students to carry for their studies rather than being dependent on the gender.  



## Question 4.What is the relationship between body weight and backpack weight?

```{r}
ggplot(backpack_data) +
  aes(x = body_weight, y = backpack_weight) +
  geom_point()+
  geom_smooth() +
  ggtitle("Relationship between body weight and backpack weight")+
  xlab("Body weight in Kg") +
  ylab("Backpack weight in Kg")
 
```

Backpack weight is not directly related to body weight.  All body weights are carrying similar weight ranges of backpacks. Some heavier body weights are carrying backpacks lower in weight than people with lower body weights.


## Question 5. Is this relationship different between men and women? Choose an appropriate plot and interpret your findings.

```{r}
ggplot(backpack_data) +
  aes(x= body_weight, y = backpack_weight, colour=sex) +
  geom_point() +
  ggtitle("Relationship between body weight and backpack weight in males and females")+
  xlab("Body weight in Kg") +
  ylab("Backpack weight in Kg")
  
```
Backpack weight is increasing slightly with body weight for both males and females.  The minimum body weights for females are lower between 100 to 125kg. The lowest body weight for males is 125Kg.



## Question 6. What proportion of students report back pain?

```{r}
ggplot(backpack_data) +
  aes(x = back_problems, colour = back_problems) +
  geom_bar() +
  theme_gray()+
  ggtitle("Number of students reporting back pain") +
  xlab("Back problems") +
  ylab("Number of students")
```

Approximately 33% of students are reporting back problems related to their backpack weights.




## Question 7. Is this proportion different between men and women?

```{r}
ggplot(backpack_data) +
  aes(x=back_problems, fill=sex) +
  geom_bar() +
  ggtitle("Proportion of men and women with back pain") +
  xlab("Back problems") +
  ylab("Number of students") +
  theme_minimal()
```
The proportion of males and females without back pain is approximately equal at almost 50% each. The proportion of males with back problems is about 25% of the total number of people with back pain.  This is much lower than the amount of females with back pain which is about 75% of the people who have back pain.



## Question 8. Now you’ve investigated your data separately, create plots to describe the relationship between backpack weight, body weight, gender and reported backpain. Try both backpack_weight and body_weight as well as the ratio.

```{r}
ggplot(backpack_data) +
  aes(x=body_weight, y=backpack_weight, fill=back_problems) +
  geom_col() +
  ggtitle("Relationship between backpack weight,body weight and reported back pain")
```

```{r}
ggplot(backpack_data) +
  aes(x=body_weight, y=backpack_weight, fill=back_problems) +
  geom_col() +
  ggtitle("Relationship between backpack weight,body weight and reported back pain")+
  facet_grid(backpack_weight~back_problems)

```
```{r}
ggplot(backpack_data) +
  aes(x= body_weight, y = backpack_weight, colour=sex) +
  geom_point() +
  ggtitle("Relationship between body weight and backpack weight in males and females")+
  xlab("Body weight in Kg") +
  ylab("Backpack weight in Kg") +
  facet_grid(backpack_weight ~ body_weight)
  
```
Males and females generally carry a similar range of backpack weights.  There is a correlation between people with higher body weights reporting less back problems. This could indicate that people who have higher body weights are better able to distribute the rucksack weight as they are carrying it and so avoid developing back problems. 
